Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-03-12 TEBenchmarkPaper/article.tex
More Wilxocon

We compare the running times of QuickSpec and IsaCoSy using a similar protocol
to the Speedup-Test of Touati, Worms and Briais~\cite{touati2013speedup}. We
differ by timing a wider variety of inputs: running many samples once, rather
than a few samples many times and taking the medians. Since each sample is run
through both tools, we can also gain statistical power by using the
\emph{paired} form of the Wilcoxon signed-rank test. We compare each sample size
is compared separately, to find the probability that QuickSpec is significantly
faster.

>>>>

We compare the running times of QuickSpec and IsaCoSy using a similar protocol
to the Speedup-Test of Touati, Worms and Briais~\cite{touati2013speedup}. We
treat each of our sample sizes as a separate ``benchmark'', but deviate from
their approach by using a different input (sample) for each run. This reduces
the sampling bias, but also reduces the accuracy of our confidence intervals.
We used version 2 of the Speedup-Test \texttt{R} implementation, which we
patched to use the \emph{paired} form of the (one-sided) Wilcoxon signed-rank
test~\cite{wilcoxon1945individual}, since this increases our statistical power
given that each sample is run through both tools. We use Pratt's
method~\cite{pratt1959remarks} to handle ties, which occur when both tools time
out.

For each sample size (``benchmark'') the Speedup-Test protocol compares the
distributions of each tool's times using a Kolmogorov-Smirnov test. If these are
significantly different (with $\alpha < 0.05$), then the signed-rank test is
only performed if more than 30 samples are available. This was the case for all
sample sizes except for 1 and 2 (due to the removed duplicates), and hence those
two speedups were not deemed statistically significant. For all other sample
sizes QuickSpec was found to be faster, with 95\% confidence. The speedup for
each size is given in table~\ref{FIXME}. The 95\% confidence interval for the
proportion of sample sizes where QuickSpec's median running time is faster than
IsaCoSy's is 66.9\% to 98.2\%.
